Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-02 paper_comparison/paper_comparison/paper_comparison.Rmd
fill in allocating subjects

Except for the parameters summarised in Table \ref{tab:model-parameter-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous.

In experiment I, II and III, three different sample sizes were selected (n = 50, 100, 300). In general, with fewer data points drawn in a residual plot, the chance of detecting the visual pattern will decrease. This can be observed from Figure \ref{fig:different-n}.

@@

Four different levels of $sigma$

```{r different-sigma, eval = FALSE, fig.cap="Example residual plots of the linear regression model used in experiment I. Four different values of $\\sigma$ are included in the experiment to control the strength of the signal."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

@@

<!-- > Experiment II -->

<!-- -   Treatments for heteroskedasticity experiment (plots summarising levels) -->

@@

>>>>

As summarised by Table \ref{tab:model-parameter-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ were used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters.

Three different sample sizes were used (n = 50, 100, 300) in all three experiments. It can be observed from Figure \ref{fig:different-n} that with fewer data points drawn in a residual plot, the visual pattern is more difficult to be detected.

@@

```{r different-sigma, fig.cap="Example residual plots of the linear regression model used in experiment I. Four different values of $\\sigma$ are included in the experiment to control the strength of the signal."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

@@

```{r different-b, fig.cap="Example residual plots of the linear regression model used in experiment II. Five different values of $b$ are included in the experiment to control the strength of the signal."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 0.25)$gen(300)

VI_MODEL$plot(ori_dat) +
  ggtitle(quote("b = 0.25")) +
  theme_light() -> p1

VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 1)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 1")) +
  theme_light() -> p2

VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 4)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 4")) +
  theme_light() -> p3

VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 16)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 16")) +
  theme_light() -> p4

VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 64)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("b = 64")) +
  theme_light() -> p5

patchwork::wrap_plots(p1, p2, p3, p4, p5, ncol = 3)
```

@@

Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in 443 different lineups. For each lineup, the actual data plot was drawn as a standard residual plot of the null model with raw residuals on the y-axis and fitted values on the x-axis. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The lineup consisted of 20 residual plots with one randomly placed actual data plot.

In addition, each lineup is designed to be evaluated by five different subjects to provide reasonable estimates of the visual p-value.

Thus, $192 \times 3 \times 5 / (20 - 2) = 160$ subjects were recruited to satisfy the design of the experiment I.

### 2022-10-02 paper_comparison/paper_comparison/paper_comparison.tex
fill in allocating subjects

\begin{verbatim}
##  [1]  TRUE FALSE  TRUE  TRUE FALSE FALSE  TRUE  TRUE  TRUE  TRUE  TRUE
\end{verbatim}

@@

Other than the parameters summarised in Table
\ref{tab:model-parameter-table}, three additional parameters \(n\),
\(\sigma\) and \(b\) were used to control the strength of the signal in
experiment I and II so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Three different sample sizes were selected (n = 50, 100,
300). In general, with fewer data points shown in a residual plot, the
chance of detecting the visual pattern will decrease. This can be
observed from Figure

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-n-1} \caption{Example residual plots of the linear regression model used in experiment I. Three different values of $n$ are included in the experiment to control the strength of the signal.}\label{fig:different-n}
\end{figure}

@@

>>>>

@@

As summarised by Table \ref{tab:model-parameter-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters.

Three different sample sizes were used (n = 50, 100, 300) in all three
experiments. It can be observed from Figure \ref{fig:different-n} that
with fewer data points drawn in a residual plot, the visual pattern is
more difficult to be detected.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-n-1} \caption{Three different values of $n$ are used in experiment I, II and III to control the strength of the signal.}\label{fig:different-n}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-sigma-1} \caption{Example residual plots of the linear regression model used in experiment I. Four different values of $\sigma$ are included in the experiment to control the strength of the signal.}\label{fig:different-sigma}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-b-1} \caption{Example residual plots of the linear regression model used in experiment II. Five different values of $b$ are included in the experiment to control the strength of the signal.}\label{fig:different-b}
\end{figure}

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in 443 different lineups. For
each lineup, the actual data plot was drawn as a standard residual plot
of the null model with raw residuals on the y-axis and fitted values on
the x-axis. The 19 null datasets were generated by the residual rotation
technique, and plotted in the same way. The lineup consisted of 20
residual plots with one randomly placed actual data plot.

Overall, we planned to collect 7974 evaluations on 1152 uniqued lineups
performed by 443 subjects throughout three experiment.

In addition, each lineup is designed to be evaluated by five different
subjects to provide reasonable estimates of the visual p-value.

Thus, \(192 \times 3 \times 5 / (20 - 2) = 160\) subjects were recruited
to satisfy the design of the experiment I.
